Crossing Origins by Crossing Formats

### 2012-11-30 main.tex
a few global edits

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
% 
This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
%
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. 
%
The paper presents novel attack vectors that are based on
\emph{syntax injection} that 
operate across multiple languages and on \emph{content repurposing} that supply
malicious payload that appears formatted as benign content. 
%
We perform a systematic study of
PDF-based injection and content repurposing attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
The existing defense mechanisms fall short to prevent these attacks
from achieving cross-domain communication.

Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content repurposing} that supply
malicious payload that appears formatted as benign content.

\todo{Say why sanitization and CSP are of no use}

\todo{Mention GIFAR and perhaps other profile examples and say we're
  the first to perform a systematic study}

We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content repurposing attacks.

@@

\paragraph{Contributions} The paper makes the following contributions:
\begin{itemize}
\vspace*{-.6cm}
\item We identify polyglot attacks, a new breed of attacks for
  crossing origins by crossing formats;
\vspace*{-.2cm}
\item We characterize the necessary ingredients for polyglot attacks
\vspace*{-.2cm}
\item We arrive at the PDF format as a particularly exposed format for
  polyglot-based attacks;
\vspace*{-.2cm}
\item We present two novel attack vectors, based on syntax and
  injection and content repurposing;
\vspace*{-.2cm}
\item We evaluate the current filtering mechanisms, browsers, and PDF
  filters for vulnerabilities; and
\vspace*{-.2cm}
\item We propose mitigation for the server, client, and PDF readers.
\end{itemize}

@@

We have identified two vectors in which malicious polyglots can be used for 
exploitation: syntax injection and content repurposing.

@@

\subsubsection{Polyglot upload}

@@

\subsection{Scenarios}

@@

\subsection{Content repurposing}
\todo{diagram with attack scenario. for example: with example domains attacker.com and
  vulnerable.com leaking secret file secret.txt}
% Description of attack technique 
A content repurposing attack targets the users of a website
that allows and serves user supplied files. Examples are a file sharing
service, an image database, or a job search service. Such a service 
accepts a limited set of file-types, and the files are verified to
be of one of these types, e.g. an image, before being served to the end
user. By submitting a polyglot to such a service, an attacker can trick the
service into serving malicious content under the origin of the service. The
service will verify the file, assuming that it is of the benign format, but once
the content is served an attacker can coerce the content to be interpreted as
the malicious format.

@@

\subsection{Content repurposing}

@@

As a content provider on the Internet today there are precautions that one can 
take to mitigate this class of vulnerabilities. Which precautions to take depend 
on the kind of services provided. The mitigation recommendations for syntax 
injection apply to services that rely on user input, and the content repurposing 
recommendations apply to services that serve user-supplied files.

@@

\subsubsection{Content repurposing}

@@

@@

\newpage
\section*{Todo}
Test page

Billy's and Jonas' anonymized demos?

>>>>

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
% 
This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
%
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. 
%
The paper presents novel attack vectors that infiltrate the trusted
origin by \emph{syntax injection} across multiple languages and by
\emph{content smuggling} of
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
  request forgery}.
%
We perform a systematic study of
PDF-based injection and content smuggling attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (in particular, PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%

Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
  request forgery}.

The existing defense mechanisms fall short to prevent these attacks
from achieving cross-domain communication. 
On the server side, santization is specific to the target language of
the web application. Sanitizing unexpected formats is typically not considered.
On the client side, CSP
has no effect unless the content is interpreted as HTML. This opens up
opportunities for attacks that are based on other formats.

First steps in exploiting the formats in the context of the web have
been by researchers. Two noteworthy examples are GIFAR~\cite{XXX} and
cross-origin CSS attacks~\cite{YYY} (Section~\ref{sec:related}
discusses further realted work). 
%
GIFAR is based on polyglots that combine the GIF and JAR (Java
archive) formats. The former is used as benign and the latter as
malicious to bypass SOP.
%
Cross-origin CSS attacks inject fragments of CSS code into an existing
web page to extract information from the existing web page.
%
The paper is the first to perform a systematic study of polyglot
attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content smuggling attacks.

@@

\paragraph{Contributions} The paper makes the following contributions:
\begin{itemize}
\vspace*{-.6cm}
\item Identification of polyglot attacks, a new breed of attacks for
  crossing origins by crossing formats;
\vspace*{-.2cm}
\item Characterization of the necessary ingredients for polyglot attacks
\vspace*{-.2cm}
\item Highlighting the PDF format as a particularly exposed format for
  polyglot attacks;
\vspace*{-.2cm}
\item Novel confidentiality and integrity attack vectors, based on syntax 
  injection and content smuggling;
\vspace*{-.2cm}
\item Evaluation of the current filtering mechanisms, browsers, and PDF
  filters for vulnerabilities; and
\vspace*{-.2cm}
\item Mitigation for the server, client, and PDF readers.
\end{itemize}

@@

We have identified two vectors in which malicious polyglots can be used for 
exploitation: syntax injection and content smuggling.

@@

\subsubsection{Content smuggling}

@@

\subsection{Exploiting the infiltrated origin}

@@

\subsection{Content smuggling}
\todo{diagram with attack scenario. for example: with example domains attacker.com and
  vulnerable.com leaking secret file secret.txt}
% Description of attack technique 
A content smuggling attack targets the users of a website
that allows and serves user supplied files. Examples are a file sharing
service, an image database, or a job search service. Such a service 
accepts a limited set of file-types, and the files are verified to
be of one of these types, e.g. an image, before being served to the end
user. By submitting a polyglot to such a service, an attacker can trick the
service into serving malicious content under the origin of the service. The
service will verify the file, assuming that it is of the benign format, but once
the content is served an attacker can coerce the content to be interpreted as
the malicious format.

@@

\subsection{Content smuggling}

@@

As a content provider on the Internet today there are precautions that one can 
take to mitigate this class of vulnerabilities. Which precautions to take depend 
on the kind of services provided. The mitigation recommendations for syntax 
injection apply to services that rely on user input, and the content smuggling
recommendations apply to services that serve user-supplied files.

@@

\subsubsection{Content smuggling}

@@

PDFAR

@@

\newpage
\section*{Todo}
Test page \url{http://internot.noads.biz} with Billy's and Jonas' anonymized demos?
